\medskip
\noindent\textbf{Experimental Setup and Test Suite}\par\smallskip
\noindent The Deployment module was verified using a focused \texttt{pytest}
test suite that exercises the module as a serving, packaging, versioning, and
orchestration component. The goal of this verification is not only to check
individual functions, but also to confirm that the deployment workflow can move
from saved artifacts and configuration files to a prepared API service in a
repeatable manner.

The test environment is intentionally isolated from external cloud services.
Temporary workspaces created with the \texttt{tmp\_path} fixture are used to
hold generated configuration files, model artifacts, VCS registries, Dockerfile
outputs, and telemetry logs. The \texttt{monkeypatch} fixture replaces external
dependencies such as subprocess calls, SSH execution, Heroku commands, and EC2
health checks. This allows the test suite to verify the correctness of the
deployment logic without requiring a live Heroku account, a running EC2
instance, or active Docker containers during every test run.

The command used to execute the deployment test suite is shown below. The
explicit \texttt{PYTHONPATH} value is important because the deployment tests
load modules both through the package path and through the isolated serving
runtime path.

\begin{lstlisting}[style=algostyle,basicstyle=\ttfamily\small,caption={Deployment test-suite execution command},label={alg:deployment_test_command}]
PYTHONPATH=accelera/src/deployment:accelera/src \
  pytest accelera/src/deployment/tests
\end{lstlisting}

This setup verifies the Deployment module in a way that is suitable for
headless execution and continuous integration. Instead of depending on the
availability of external platforms, the tests check that Accelera generates the
correct files, calls the correct commands, validates inputs correctly, records
telemetry correctly, and preserves model snapshots correctly.

\medskip
\noindent\textbf{Verification Objectives}\par\smallskip
\noindent The Deployment module contains several responsibilities that must
work together. Table~\ref{tab:deployment_verification_objectives} summarizes
the main verification objectives used in the test suite. The table is included
before the detailed results to show how each group of tests supports a concrete
quality requirement of the module.

\acceleraTableStyle
\begin{longtable}{>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.32\textwidth}
  >{\raggedright\arraybackslash}p{0.33\textwidth}}
\caption{Deployment module verification objectives.}
\label{tab:deployment_verification_objectives}\\
\toprule
\textbf{Objective} & \textbf{Reason} & \textbf{Evidence in tests} \\
\midrule
\endfirsthead
\caption[]{Deployment module verification objectives (continued).}\\
\toprule
\textbf{Objective} & \textbf{Reason} & \textbf{Evidence in tests} \\
\midrule
\endhead
\midrule
\multicolumn{3}{r}{\small Continued on the next page}\\
\endfoot
\bottomrule
\endlastfoot
Artifact reproducibility &
The deployed service must be based on known model files and a known
configuration. &
VCS tests check commit creation, parent links, \texttt{HEAD}, deployed markers,
and rollback restoration. \\
\midrule
Serving correctness &
The service must load models and preprocessors in the expected order before
prediction. &
Model service tests load serialized artifacts, verify idempotent loading, and
check preprocessing before prediction. \\
\midrule
Input reliability &
Invalid payloads must be rejected before reaching the model. &
Schema validation tests cover missing columns, unexpected columns, type
coercion, booleans, integers, numeric ranges, and allowed values. \\
\midrule
API behavior &
The deployed service must expose predictable routes for prediction, health,
GUI, CSV upload, and tracking. &
Server tests verify successful responses, validation errors, internal errors,
row counting, GUI rendering, and tracking summary behavior. \\
\midrule
Operational repeatability &
Deployment commands must produce correct Docker, Heroku, and EC2 command
flows. &
Orchestration tests inspect Docker build/run calls, Heroku sequencing, SSH
transport, remote scripts, \texttt{rsync}, stop, and log commands. \\
\end{longtable}

\medskip
\noindent\textbf{Subsystem Verification Details}\par\smallskip
\noindent The test suite targets the major components of the Deployment module:
model VCS, model loading, runtime validation, API serving, telemetry, and
deployment orchestration. These components were tested separately because each
one represents a failure point in a real deployment workflow.

\begin{enumerate}[leftmargin=*]
  \item \textbf{Model Version Control verification:}
  The VCS tests verify the stability of short SHA-1 commit identifiers, prefix
  resolution, index save/load behavior, workspace initialization, commit
  creation, parent tracking, log formatting, status reporting, and deployment
  rollback. The most important result is that committed model artifacts and
  configuration files can be restored into the active deployment workspace,
  which supports repeatable deployment and rollback.

  \item \textbf{Model Service verification:}
  The \texttt{ModelService} tests verify that the service reads
  \texttt{config.json}, loads serialized preprocessors and models, identifies
  the predict-capable artifact, and applies preprocessing before prediction.
  They also verify that loading is idempotent and that a clear runtime error is
  raised when no loaded artifact supports prediction.

  \item \textbf{Runtime Schema Validation verification:}
  The schema tests verify both disabled and enabled validation modes. They
  confirm that missing columns and unexpected columns are detected, that numeric
  and integer values are coerced safely, that boolean representations are
  normalized, and that invalid values produce structured validation errors.
  These checks are important because the deployed API must protect the model
  from malformed inputs.

  \item \textbf{Web Serving Endpoints verification:}
  The server tests verify the behavior of the FastAPI routes without requiring
  a live server process. They check that the root path redirects to the GUI,
  that \texttt{/health} and \texttt{/tracking/summary} report service state,
  that missing prediction input is rejected, that successful predictions record
  telemetry events, and that validation or internal errors map to the expected
  HTTP error behavior.

  \item \textbf{Prediction Tracking verification:}
  The telemetry tests verify that a disabled tracker performs no writes, while
  an enabled tracker writes valid JSON lines and can summarize request counts,
  total rows, status counts, and the last recorded event. This confirms that
  the deployed service has a lightweight observability layer rather than only a
  prediction endpoint.

  \item \textbf{Deployment Orchestration verification:}
  The orchestration tests verify the command-building and file-generation logic
  of \modulepath{deployment.py}. They check valid and invalid ports, model path
  validation, service-source synchronization, generated \texttt{requirements.txt},
  generated \texttt{Dockerfile}, Docker build and run commands, Heroku
  deployment order, SSH configuration, remote EC2 script generation,
  \texttt{rsync} synchronization, EC2 deployment flow, and remote stop/log
  operations.
\end{enumerate}

\medskip
\noindent\textbf{Command-Flow Verification}\par\smallskip
\noindent In addition to unit-level behavior, the tests verify important
command flows that a user would execute during deployment. This is significant
because deployment failures often happen not inside model inference, but in the
surrounding operational steps: building containers, selecting ports,
synchronizing files, and starting services on remote hosts.

Table~\ref{tab:deployment_command_flow_results} summarizes the command flows
covered by the orchestration tests. The table shows that the Deployment module
was tested as an operational tool, not only as a collection of Python helper
functions.

\begin{table}[H]
\centering
\acceleraTableStyle
\caption{Verified deployment command flows.}
\label{tab:deployment_command_flow_results}
\begin{tabularx}{\textwidth}{p{0.26\textwidth}X X}
\toprule
\textbf{Flow} & \textbf{Verified behavior} & \textbf{Result} \\
\midrule
Local Docker build &
The build command includes Docker build arguments, image naming, and optional
cache bypass. &
Command construction passed. \\
\midrule
Local Docker run &
The module checks for containers already publishing the selected port, stops
conflicting containers, and starts a new mapped container. &
Port-handling flow passed. \\
\midrule
Heroku deployment &
The complete deployment sequence runs login, optional app creation, container
login, push, release, and open in the expected order. &
Heroku orchestration passed. \\
\midrule
EC2 remote deployment &
The module prepares files, creates the remote directory, synchronizes build
inputs, runs the remote deployment script, and checks the public URL. &
EC2 orchestration passed. \\
\midrule
EC2 operations &
The stop and logs commands generate the expected remote Docker operations. &
Operational commands passed. \\
\bottomrule
\end{tabularx}
\end{table}

\medskip
\noindent\textbf{Deployment Test Results}\par\smallskip
\noindent When the deployment test suite is executed in an environment with the
required Python dependencies available, all 48 test cases pass. The result is a
strong indication that the module's core responsibilities are implemented
consistently: artifacts are versioned, models are loaded, inputs are validated,
API behavior is predictable, telemetry is recorded, and deployment commands are
generated correctly.

Table~\ref{tab:deployment-test-summary} presents the final test distribution.
The table is organized by test file so that each subsystem can be traced back
to its verification source in the repository.

\begin{table}[H]
\centering
\acceleraTableStyle
\scriptsize
\caption{Deployment Module Test Suite Verification Summary}
\label{tab:deployment-test-summary}
\begin{tabularx}{\textwidth}{p{0.29\textwidth}rrrX}
\toprule
\textbf{Test File} & \textbf{Cases} & \textbf{Passed} & \textbf{Failed} & \textbf{Verified Feature} \\
\midrule
\texttt{vcs\_test.py} & 16 & 16 & 0 & Registry snapshots, \texttt{HEAD}, status, and rollback restoration \\
\texttt{modelservice\_test.py} & 5 & 5 & 0 & Artifact loading, idempotent loading, and preprocessor sequencing \\
\texttt{schema\_validation\_test.py} & 3 & 3 & 0 & Schema description, missing-column checks, and unexpected-column reporting \\
\texttt{server\_test.py} & 8 & 8 & 0 & FastAPI routes, prediction responses, GUI rendering, and telemetry events \\
\texttt{tracking\_test.py} & 3 & 3 & 0 & JSONL telemetry writing and summary aggregation \\
\texttt{deployment\_test.py} & 13 & 13 & 0 & Docker, Heroku, SSH, EC2, model-path, and generated-file workflows \\
\midrule
\textbf{Total} & \textbf{48} & \textbf{48} & \textbf{0} & \textbf{All deployment checks passed} \\
\bottomrule
\end{tabularx}
\end{table}

\noindent The successful result confirms that the Deployment module operates as
a reliable final stage for Accelera. It does not merely save model files; it
validates the artifacts needed for serving, builds a deployable runtime
package, protects inference through schema validation, exposes API behavior,
records prediction activity, and verifies the command paths needed for local
and remote deployment. This strengthens Accelera's position as an end-to-end
machine-learning system that continues beyond training and evaluation into
practical service delivery.
